Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Quote title

In the ISAF International Umpire's and Match Racing Manual \cite{isaf}, section
M.2 Recommended Criteria for Round Robin Pairing Lists, the following criteria
are given:

>>>>

In the ISAF ``International Umpire's and Match Racing Manual'' \cite{isaf}, section
M.2 Recommended Criteria for Round Robin Pairing Lists, the following criteria
are given:
